Brownian Dynein Model

### 2015-08-12 latex/derivation.tex
Add rudimentary tests and notes for more tests to write.
a few tweaks while meeting

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{bl} &= 0 \\
  X_{ml} &= X_{bl}+L_{s}\cos(\Theta_{bl}) \\
  X_{t}  &= X_{ml}+L_{t}\cos(\Theta_{ml}) \\
  X_{mr} &= X_{t} +L_{t}\cos(\Theta_{mr}-\pi) = X_{t} + \mn L_{t}\cos(\Theta_{mr}) \\
  X_{br} &= X_{mr}+L_{s}\cos(\Theta_{br}-\pi) = X_{mr}+ \mn L_{s}\cos(\Theta_{br})
\end{align}

@@

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) =
\dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
+ \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\end{multline}

>>>>

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{bl} &= 0 \\
  X_{ml} &= X_{bl}+L_{s}\cos(\Theta_{bl}) \\
  X_{t}  &= X_{ml}+L_{t}\cos(\Theta_{ml}) \\
  X_{mr} &= X_{t} - L_{t}\cos(\Theta_{mr}) \\
  X_{br} &= X_{mr} - L_{s}\cos(\Theta_{br})
\end{align}

@@

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) =
\dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
+ \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\end{multline}%Fix'd
